\documentclass{package/notes}
\usepackage[english]{babel}
\usepackage{amssymb,amsmath,amsfonts}  %%% for maths
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{package/color-env}
\usepackage{lipsum}
\usepackage{graphicx}
\renewcommand\qedsymbol{$\blacksquare$}

\newcommand{\F}{\sum F}
\newcommand{\m}{\text{ m}}
\newcommand{\km}{\text{ km}}
\newcommand{\cm}{\text{ cm}}
\newcommand{\s}{\text{ s}}
\newcommand{\kg}{\text{ kg}}
\newcommand{\N}{\text{ N}}
\newcommand{\J}{\text{ J}}
\newcommand{\W}{\text{ W}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

	\begin{titlepage} % Suppresses headers and footers on the title page
		
		\centering % Centre everything on the title page
		
		\scshape % Use small caps for all text on the title page
		
		\vspace*{\baselineskip} % White space at the top of the page
		
		%------------------------------------------------
		%	Title
		%------------------------------------------------
		
		\rule{\textwidth}{1.6pt}\vspace*{-\baselineskip}\vspace*{2pt} % Thick horizontal rule
		\rule{\textwidth}{0.4pt} % Thin horizontal rule
		
		\vspace{0.75\baselineskip} % Whitespace above the title
		
		{\huge PHYS103: General Physics I Notes} % Title
		
		\vspace{0.75\baselineskip} % Whitespace below the title
		
		\rule{\textwidth}{0.4pt}\vspace*{-\baselineskip}\vspace{3.2pt} % Thin horizontal rule
		\rule{\textwidth}{1.6pt} % Thick horizontal rule
		
		\vspace{2\baselineskip} % Whitespace after the title block
		
		%------------------------------------------------
		%	Subtitle
		%------------------------------------------------
		
		\LARGE{} 
		
		\vspace*{3\baselineskip} % Whitespace under the subtitle
		
		
		
		\vspace{0.5\baselineskip} 
		
		{\scshape   \LARGE Professor David James\\ } % Editor list
		
		\vspace{0.5\baselineskip}
		
		\vfill 
		
		%------------------------------------------------
		% Author
		%------------------------------------------------
		
		
		\vspace{0.3\baselineskip} 
		
		
		{\large Edited by\\  Trevor Bushnell} 
		
	\end{titlepage}
	\tableofcontents
%\newpage
\chapter*{Introduction}

This document aims to highlight the important content of the PHYS103 course in traditional notes format. These notes are completely open-source, which means anyone is allowed to use these notes for their own personal benefit without having to seek permission from myself. \newline

While these notes are designed for the PHYS103 course, all of the content seen in these notes are equivalent to a one-semester calculus-based introductory physics class taken at many universities. The content in these notes might also have some overlap with the AP Physics C: Mechanics Course. As such, students in the AP Physics C: Mechanics course and students taken any calculus-based introductory physics course might still find the content provided in these notes useful.\newline

Due to the open-source nature of these notes, anyone is allowed to contribute to improving these notes as they see fit. Since I am using GitHub to distribute these notes easily, you must request all changes through the repository website on GitHub, which you can find \textbf{here}. If you are interested in contributing to these notes, then there are a few ways that you can do so:\newline

\begin{enumerate}
	\item \textbf{Open and submit an issue on my GitHub repository:} I write all my notes in \LaTeX, which is a typesetting language that is really helpful when it comes to typing and rendering math equations quickly and easily. If you do not know how to write \LaTeX code but are still interested in making a change to the notes, you can open an issue by going to the MathNotes repo on GitHub, and clicking on the button labeled "New Issue." From there, you can type out the change that you wish to see in the notes. It would be helpful if you would indicate what course you would like to see changed so that I can understand what you are referring to. I will then update the code to include your issue so that you don't have to worry about writing the code yourself.
	\item \textbf{Create and submit a pull request:} If you know how to write LaTeX code and you understand how GitHub works, you can submit a pull request where you can write the code that you want to change yourself. I will then review the code and either submit the code to be incorporated into the notes OR provide some comments on your code if I wish for something to be different. 
\end{enumerate}\newpage

Thank you so much for using these notes. I hope that the information is provided in such a way that it can help you when reviewing content for you homework, quizzes, and exams and just in general when it comes to learning the content for the course. Happy studying!

\newpage


\chapter{Measurement and Vectors}
\input{chapters/ch1/Unit1.tex}


\chapter{Kinematics}
\input{chapters/ch2/Unit2.tex}


\chapter{Forces}
\input{chapters/Unit3.tex}


\chapter{Work and Energy}
\input{chapters/ch4/Unit4.tex}

\chapter{TEST \#2 REVIEW}

\section{Friction}

\begin{itemize}
    \item The static friction force and the applied force are going to be equal until a certain breakaway point
    \item Once we pass the “friction breaking point”, then we get kinetic friction which becomes a CONSTANT force
    \item Because there are two types of friction forces, DON’T SIMPLY SAY $F_f = \mu F_n$!!!
\end{itemize}


\section{Centripetal Forces}

\begin{itemize}
    \item Centripetal forces are forces that cause an object to continue moving in a circle
    \item this means that Newton’s Second Law becomes $F=ma_c$
    \item Centripetal forces always point towards the CENTER of the circle
    \begin{itemize}
        \item This means that at the top of the circle, the centripetal force points down
        \item at the bottom of the circle, the centripetal force points up
    \end{itemize}
\end{itemize}


\section{Work}

\begin{itemize}
    \item $W = F \cdot d$
    \item SI Units: Joules
    \item If the applied force is not constant, then you know that $W = \int F(x)dx$
    \begin{itemize}
        \item Note that you may not have to calculate an integral, but you should know that if you have a graph of Force as a function of distance and you are being asked to find work, then you should compute the \textbf{area under the curve}
    \end{itemize}
\end{itemize}


\section{Energy}

\begin{itemize}
    \item If work is being done on an object, then the object has some energy
    \item \textbf{Kinetic Energy:} energy if the object is in motion: $KE = \FRAC{1}{2}mv^2$
    \item \textbf{Gravitational Potential Energy:} energy if the object is hovering in the air: $PE = mgh$
    \item \textbf{Spring Energy:} energy if the object compresses the spring
    \item \textbf{Thermal Energy:} Energy that is lost to heat to the environment
    \item $W = \Delta KE + \Delta PE + \Delta E_s + E_{TH}$
    \item If no external forces are applied on the system, then the net work of the system is ZERO
\end{itemize}

\section{Test Question Examples}

\begin{problem}
    A block of mass $m$ is pushed off a spring with spring constant $K$ which was compressed a distance $\Delta x$. The block moves up a slope that is $H$ meters high, then returns to ground level and slides across a source of friction with coefficient of kinetic friction $\mu_k$. \\
    
    a) What is the speed of the block just after the block starts moving after the spring initially pushes the block off?
    
    $$
    \begin{aligned}
        W &= \Delta KE + \Delta PE + \Delta E_s + E_{TH}\\
        0 &= \frac{1}{2}mv_A^2 + \frac{1}{2}K(-\Delta x^2)\\
        v_A &= \sqrt{\frac{K}{m}\Delta x^2}
    \end{aligned}
    $$
    
    b) What is the speed of the block at the top of the slope?
    
    $$
    \begin{aligned}
        W &= \Delta KE + \Delta PE + \E_s + E_{TH}\\
        0 &= \frac{1}{2}mv_B^2+mgH + \frac{1}{2}K(-\Delta x^2)\\
        v_B &= \sqrt{\frac{K\Delta x^2 - mgH}{m}}
    \end{aligned}
    $$
    
    c) How far does the block slide on the friction surface before the block stops?
    
    $$
    \begin{aligned}
        W &= \Delta KE + \Delta PE + \Delta E_s + E_{TH}\\
        0 &= \frac{1}{2}m(-v_B^2) + mg(-H) + F_fL\\
        0 &= \frac{1}{2}m(-v_B^2) + mg(-H) + \mu_kmgL\\
        L &= \frac{\frac{1}{2}mv_B^2+gH}{\mu_kg}
    \end{aligned}
    $$
\end{problem}

\section{WHAT IS ON THE EXAM TOMORROW}

\begin{itemize}
    \item Spud Gun
    \item Car
    \item Siding Block
    \item Graph
    \item Ramp/Spring/Box
    \item BONUS: Quadratic Equation
\end{itemize}



\end{document}